\documentclass[12pt]{article}

\usepackage[margin=0.5in]{geometry} % Change margins
\usepackage{xcolor} % Custom color
\usepackage{times} % Change font
\usepackage{nopageno}
\usepackage{enumitem} % Allow custom itemize bullet character

\usepackage[colorlinks = true,
            linkcolor  = blue,
            urlcolor   = blue,
            citecolor  = blue,
            anchorcolor= blue]{hyperref} % Links at top


\definecolor{textGray}{RGB}{75, 78, 80}
\newcommand{\sectionRule}{\textcolor{gray}{\rule{7.27in}{0.02cm}}}
\newcommand{\sectionTxt}[1]{\noindent\textbf{#1}\\}
\newcommand{\textDate}[3]{\noindent#1 $|$ #2 $|$ {\color{textGray} #3}}
\newcommand{\projText}[2]{\noindent#1 $|$ {\color{textGray} #2}}


\begin{document}
    \begin{center}
        {\huge Sammy Al Hashemi}\\
        {\normalsize 917.846.6665 $|$ sammyalhashemi1@outlook.com}\\
        {\normalsize LinkedIn: \href{https://www.linkedin.com/in/sammyalhashemi}{linkedin.com/in/sammyalhashemi} $|$ GitHub: \href{https://github.com/Sammyalhashe}{github.com/Sammyalhashe}}\\
    \end{center}
    \sectionTxt{TECHNICAL SKILLS}
    \sectionRule
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item Proficient: {\color{textGray}C++, Python, Zig, Linux}
            \item Exposure: {\color{textGray}C, Bash Scripting, Makefile/Cmake, Functional Ocaml, Typescript/Javascript, Java}
        \end{itemize}
    \end{small}
    \sectionTxt{WORK EXPERIENCE}
    \sectionRule

    \textDate{Bloomberg}{Software Engineer}{Present}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {\color{textGray} Worked on the design and implementation of an existing internal pub/sub middleware system that streamlines data from backend to frontend on Bloomberg's terminal}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {\color{textGray} This product is the driving force behind delivering dynamic data to Bloomberg's clients.}
                \end{itemize}
            \item {\color{textGray} Worked with sister teams to integrate their routing and entitlement products into the pub/sub framework.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {\color{textGray} Reorganized the internal mechanisms of how the pub/sub framework currently handles routing to account for this new routing logic.}
                    \item {\color{textGray} Added shared libraries that multiple tasks link in to provide entitlement information when needed to enhance infrastructure security.}
                \end{itemize}
            \item {\color{textGray} Introduced a methodology that would allow application developers using the pub/sub framework to quickly "unblock" their application when their application crashes.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {\color{textGray} This saves application developers' time by allowing them to bypass typical administrative approvals.}
                \end{itemize}
        \end{itemize}
    \end{small}


    \textDate{MThree (Contracted to Morgan Stanley)}{Software Developer}{Aug 2019 -- Aug 2020}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {\color{textGray} Developed a javascript and Angular 6 frontend to provide users with streamlined experience when working through internal entitlement management workflow.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {\color{textGray} Optimized the process from a 3-week stretch to ~3 days.}
                \end{itemize}
            \item {\color{textGray} Engineered a backend java server to handle 500+ ticket requests weekly as well as interfacing with internal APIs for the entire entitlement system utilizing Spring Boot.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {\color{textGray} Saved the company approximately \$4400 in employee hours monthly.}
                \end{itemize}
            \item {\color{textGray} Maintained a frontend javascript testing framework built wiht Protractor and Selenium to test new feature scenarios, reducing bug rate by close to 5\%.}
        \end{itemize}
    \end{small}

    \textDate{Microsemi}{Device Characterization Engineer (Intern)}{Jun 2017 -- Aug 2018}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {\color{textGray} Built test structures and designs to characterize multiple components of Microsemi's G5 FPGA architecture, such as its Mathblock and AC components using Verilog and Microsemi's FPGA programming software.}
            \item {\color{textGray} Constructed drivers for tests in an internal java-based language to test multiple scenarios important to the validation of the FPGA component being tested.}
                \begin{itemize}[label=$\circ$,topsep=-5px,partopsep=0px]
                    \itemsep0em 
                    \item {\color{textGray} Saved the company approximately \$4400 in employee hours monthly.}
                \end{itemize}
            \item {\color{textGray} Maintained a frontend javascript testing framework built wiht Protractor and Selenium to test new feature scenarios, reducing bug rate by close to 5\%.}
        \end{itemize}
    \end{small}

    \sectionTxt{EDUCATION}
    \sectionRule

    \textDate{B.S. Engineering Science (Physics)}{University of Toronto}{Sept 2014 -- June 2019}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item Relevant Coursework: {\color{textGray} Algorithm Design, Data structures and Algorithms, Partial Differential Equations and Vector Calculus, Machine Learning and Data Mining.}
        \end{itemize}
    \end{small}

    \sectionTxt{PROJECT WORK}
    \sectionRule

    \textDate{Final Year Undergraduate Thesis}{2019}{\href{https://github.com/Sammyalhashe/Thesis/tree/master/Grover}{Code URL}}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {\color{textGray} Analyzed validity and feasibility of practical quantum search.}
            \item {\color{textGray} Using various quantum computing platforms and SDK's like IBM qiskit, I programmed scalable models of Grover's famous quantum search algorithm to analyze its real-world practicality.}
            \item {\color{textGray} Through my analysis of my various implementations of Grover's algorithm and their timing and hardware requirements, it was determined that we do no have the capability to implement scalable versions of Grover's algorithm today, and its practicality may be hindered by its requirement of a quantum oracle function.}
        \end{itemize}
    \end{small}

    \textDate{Physics Lab Data Recorder}{Feb 2020 -- Mar 2020}{\href{https://github.com/Sammyalhashe/Charter-cp}{Code URL}}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {\color{textGray} Using PyQt5, in a team of three I built a charting application that reads data interfaced from an \textit{ni daqmx} board as well as general serial ports.}
            \item {\color{textGray} Pyqtgraph was used to implement the charting visual, and the users are able to record data, stop, resume, and save the data to csv (as well as an image), and transform the data with Fast Fourier Transform and other logarithmic transforms.}
        \end{itemize}
    \end{small}

    \textDate{Gameboy Emulator}{In progress}{\href{https://github.com/Sammyalhashe/GameboyEmulator}{Code URL}}
    \begin{small}
        \begin{itemize}
            \itemsep0em 
            \item {\color{textGray} Written in C++, currently I have completed the CPU OPCODES. Next step is handling the interrupts and timing.}
        \end{itemize}
    \end{small}

    \sectionTxt{LEADERSHIP + AWARDS}
    \sectionRule

    \begin{small}
        \begin{itemize}
            \itemsep0em
            \item {\color{textGray} \textDate{University of Toronto}{2019}{\textit{Faculty of Applied Science and Engineering - Graduated with honours}}}
            \item {\color{textGray} \textDate{Tennis Canada}{2010}{\textit{Achieved a career high ranking of 24th in Canada}}}
        \end{itemize}
    \end{small}

\end{document}
