\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bloomberg}{Jan 2024 -- Present}
      {Senior Software Engineer}{New York, NY}
    \resumeSubheading
      {}{Jan 2020 -- Jan 2024}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented an internal \textbf{C++} pub/sub middleware streaming millions of real-time market data updates per second to Bloomberg Terminal clients across IB, MSG, and GP products.}
          \begin{itemize}[leftmargin=0.3in]
            \item\small{Added two-way metadata exchange, enabling subscribers to modify subscription parameters at runtime without reconnecting.}
            \item\small{Refactored the settings pipeline to return arbitrary JSON from the database, eliminating coordinated schema changes across processes when adding new configuration fields.}
          \end{itemize}
          \vspace{-4pt}
        \resumeItem{Integrated company-wide routing and entitlement libraries into the framework, replacing per-team configuration with a unified request-routing and access-control layer as part of an org-level standardization initiative.}
        \resumeItem{Built and maintained a Cython binding layer exposing the C++ SDK to Python consumers; became one of Bloomberg's most widely used internal libraries, adopted by 50+ application teams for middleware integration.}
        \resumeItem{Exposed the pub/sub framework to web clients over HTTP via an nginx reverse proxy with JWT-secured JSON transport.}
        \resumeItem{Designing an OpenAPI specification and JavaScript client SDK to standardize web-client integration across Bloomberg.}
        \resumeItem{Wrote a \textbf{Python} bot that automatically triages $\sim$100 false-positive tickets per week via Kafka and batched HTTP requests, eliminating a recurring manual workload for the team.}
        \resumeItem{Presented technical talks at Bloomberg's internal conference and C++ guild (see Talks section).}
      \resumeItemListEnd

    \resumeSubheading
      {MThree (Contracted to Morgan Stanley)}{Aug 2019 -- Aug 2020}
      {Software Developer}{New York, NY}
      \resumeItemListStart
        \resumeItem{Engineered a Java/Spring Boot backend handling 500+ entitlement ticket requests weekly, interfacing with internal APIs across the entitlement system.}
        \resumeItem{Developed an Angular 6 frontend and maintained a Protractor/Selenium test suite ensuring end-to-end coverage of the entitlement workflow.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
